Studying measurement invariance in factor analysis models via stochastic processes

### 2011-02-08 MIpaper/par_instable.tex
New figure of simulation results
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@36 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

In summary, we found that the proposed tests have adequate power to detect
measurement invariance violations in applied contexts.  The specific
statstics' are not equivalent to one another, and we found that the
Cram\`{e}r-von Mises statistic exhibited the best performance for the
data generated here.  In the discussion, we consider the extent to
which these findings may extend to other factor-analytic situations.

% Need to modify table and add figure
\begin{table*}
\caption{Simulated power and Type I error rates for four test statistics
  across three sample sizes and four magnitudes of measurement
  invariance violations. Abbreviations: CvM = Cram\'{e}r-von Mises
  test; MLM = Maximum Lagrange multiplier test; DM = Double-max test; 
  $\chi^2$ = Chi-square likelihood ratio test.}
\label{tab:sim1}
\begin{tabular}{llcccc} \thickline
 & & \multicolumn{4}{c}{Violation Magnitude (SEs)} \\
$n$ & Test Stat & 0 & 1 & 2 & 3 \\\hline
100 & CvM       & 0.05 & 0.10 & 0.33 & 0.63 \\ 
    & MLM       &      & 0.09 & 0.28 & 0.64 \\
    & DM        & 0.03 & 0.06 & 0.19 & 0.41 \\ 
    & $\chi^2$  & 0.07 & 0.16 & 0.49 & 0.83 \\ \hline
200 & CvM       & 0.05 & 0.19 & 0.64 & 0.96 \\
    & MLM       &      & 0.19 & 0.63 & 0.96 \\ 
    & DM        & 0.03 & 0.12 & 0.44 & 0.88 \\ 
    & $\chi^2$  & 0.06 & 0.27 & 0.76 & 0.99 \\ \hline
500 & CvM       & 0.05 & 0.44 & 0.98 & 1.00 \\ 
    & MLM       &      & 0.41 & 0.99 & 1.00 \\
    & DM        & 0.04 & 0.35 & 0.94 & 1.00 \\ 
    & $\chi^2$  & 0.05 & 0.58 & 1.00 & 1.00 \\\thickline
\end{tabular}
\end{table*}

>>>>

In summary, we found that the proposed tests have adequate power to detect
measurement invariance violations in applied contexts.  The 
Cram\`{e}r-von Mises statistic exhibited the best performance for the
data generated here, though this result may not hold for all
situations.  In the discussion, we specifically consider the extent to 
which these findings may extend to other factor-analytic situations.

\begin{figure}
\caption{Simulated power for three test statistics across three sample
  sizes, two subsets of tested parameters, and measurement invariance
  violations of 0 to 5 standard 
  errors.  Circles reflect the double-max test, triangles reflect the
  max-LM test, and plus signs reflect the Cram\`{e}r-von Mises test.
  Numbers above each panel reflect the sample size and number of
  parameters being tested, respectively.}
\label{fig:simres}
\includegraphics[height=5in]{simres.pdf}
\end{figure}

% Need to modify table
\begin{table*}
\caption{Simulated power and Type I error rates for four test statistics
  across three sample sizes and four magnitudes of measurement
  invariance violations. Abbreviations: CvM = Cram\'{e}r-von Mises
  test; MLM = Maximum Lagrange multiplier test; DM = Double-max test; 
  $\chi^2$ = Chi-square likelihood ratio test.}
\label{tab:sim1}
\begin{tabular}{llcccc} \thickline
 & & \multicolumn{4}{c}{Violation Magnitude (SEs)} \\
$n$ & Test Stat & 0 & 1 & 2 & 3 \\\hline
100 & CvM       & 0.05 & 0.10 & 0.33 & 0.63 \\ 
    & MLM       &      & 0.09 & 0.28 & 0.64 \\
    & DM        & 0.03 & 0.06 & 0.19 & 0.41 \\ 
    & $\chi^2$  & 0.07 & 0.16 & 0.49 & 0.83 \\ \hline
200 & CvM       & 0.05 & 0.19 & 0.64 & 0.96 \\
    & MLM       &      & 0.19 & 0.63 & 0.96 \\ 
    & DM        & 0.03 & 0.12 & 0.44 & 0.88 \\ 
    & $\chi^2$  & 0.06 & 0.27 & 0.76 & 0.99 \\ \hline
500 & CvM       & 0.05 & 0.44 & 0.98 & 1.00 \\ 
    & MLM       &      & 0.41 & 0.99 & 1.00 \\
    & DM        & 0.04 & 0.35 & 0.94 & 1.00 \\ 
    & $\chi^2$  & 0.05 & 0.58 & 1.00 & 1.00 \\\thickline
\end{tabular}
\end{table*}
